---
title: "Bank Acquisition and Attrition models"
author: "Apoorva_Reddy_Adavalli"
date: "24 March 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Trying to find answers for the following questions:
Do demographics, such as age and income influence acquisition probability?
Are people who have taken loans before more likely to open a new account?
Do geographical variables and market shares matter?

## Prediction- To predict probability/likelihood to acquire a customer 

##Binomial models - Logit and Probit 

```{r cars}
bac=read.csv("D:/UT_Austin/Spring/marketing/Bank/Bank_customer_acquisition.csv",header=T)
head(bac)
```

Implementing logistic regression (using logit and probit links in glm)
```{r}
bac.glm1= glm (Acquisition~Age+Income+HomeVal+LoanInd+Dist2Bank+MktShare, data=bac, family=binomial(link="logit"))
bac.glm2 = glm(Acquisition~Age+Income+HomeVal+LoanInd+Dist2Bank+MktShare, data=bac, family=binomial(link="probit"))
```
Model comparision between logit and probit of binomial family of models implemented above
```{r}
AIC(bac.glm1)
BIC(bac.glm1)
AIC(bac.glm2)
BIC(bac.glm2)
```
Very similar performance can be noticed.

```{r}
bac.pred1 = predict(bac.glm1, type="response")
cat(" Correlation between predicted and actual in case of logit link:", cor(bac$Acquisition, bac.pred1))
```

```{r}
bac.pred2 = predict(bac.glm2, type="response")
cat(" Correlation between predicted and actual in case of probit link:", cor(bac$Acquisition, bac.pred2))
```
Very similar performance can be noticed (like in case of AIC and BIC)

##Hierarchical Generalized Linear Models (HGLM) with random effects 

```{r}
#Bayesian modeling fitting
library(MCMCpack)
bac.bp = MCMCprobit(Acquisition~Age+Income+HomeVal+LoanInd+Dist2Bank+MktShare, data=bac, mcmc=6000)
summary(bac.bp)
```

```{r}
bac.ba2 = MCMChlogit(fixed=Acquisition~Age+Income+HomeVal+LoanInd+Dist2Bank+MktShare, random=~Income, group="CustomerID", data=bac, mcmc=6000, r=2, R=diag(2))
```
```{r}
summary(bac.ba2$mcmc[,1:7])
```

##Binary Data Regression Models for Bank Customer Attrition
2505 customers, among whom 449 (about 18%) have closed their accounts within one year. I would like to know what
demographic and behavioral variables contribute to higher attrition/churn rates among these customers. 

```{r}
bank.data = read.csv("Bank_Retention_Data.csv", header=T)
bank$TractID = as.factor(bank.data$TractID)
bank.logit1 = glm(Churn~Age+Income+HomeVal+Tenure+DirectDeposit+Loan+Dist+MktShare, data=bank.data,
                  family=binomial(link="logit"))
summary(bank.logit1)

```

```{r}
head(bank.data)
```

```{r}
bank.probit1 = glm(Churn~Age+Income+HomeVal+Tenure+DirectDeposit+Loan+Dist+MktShare, data=bank.data,
                   family=binomial(link="probit"))
summary(bank.probit1)
```

```{r}

AIC(bank.logit1)
BIC(bank.logit1)

AIC(bank.probit1)
BIC(bank.probit1)
```
There isn't a big difference in AIC and BIC. However if you observe precisely, we can infer that Probit fits a little
better than Logit. 

Next we will use a random effect grouped by TractID in the logistic regression
# Random Effects Model - TractID
```{r}
library(lme4)
library(scales)
bank$Age<-rescale(bank$Age)
bank$HomeVal<-rescale(bank$HomeVal)
bank.glmer = glmer(Churn ~ Age+Income+HomeVal+Tenure+DirectDeposit+Loan+Dist+MktShare+ (1|TractID),
                   data = bank, family=binomial(link="logit"), glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)))
summary(bank.glmer)

```

Model Performance in case of Random Effects
```{r}
AIC(bank.glmer)
BIC(bank.glmer)
```

Insights: 
The significant betas are still the same even in the case of random effects models. Loan & MktShare came out
to not significant like in the above models.
The AIC and BIC increased in the random effects model as shown above. Thus, this model with random effects
Doesn't fit well compared to the above logit and probit models.

```{r pressure, echo=FALSE}
plot(pressure)
```

## Bayesian Estimation in Heirarchical Modelling 
```{r}
library(MCMCpack)
bank1 = read.csv("Bank_Retention_Data.csv", header=T)
bank1_bayesian =MCMChlogit(fixed=Churn~Age+Income+HomeVal+Tenure+DirectDeposit+Loan+Dist+MktShare, random=~1,
             group="TractID", data=bank1, mcmc=20000, burnin=10000,thin=20, r=2, R=1)
summary(bank1_bayesian$mcmc[,1:9])
```

## Survival Model

```{r}
bankdata = read.csv(file = "Bank_Attrition_Data.csv", header=T)
head(bankdata)

```

```{r}
bankdata$TractID = as.factor(bankdata$TractID)
dim(bankdata)
bank.lst = list()
remainCMR = rep(0, 12)
churnCMR = rep(0, 12)
for(m in 1:12) {
  bank.lst[[m]] = bankdata[bankdata$Month==m,]
  remainCMR[m] = dim(bank.lst[[m]])[1]
  churnCMR[m] = sum(bank.lst[[m]]$Churn==1)
}
churnRate = churnCMR/remainCMR
#bank.lst
cat("MoM retained customers", remainCMR,"\n")
cat("MoM churned customers", churnCMR)
```


```{r}

bank.logit= glm(Churn~as.factor(Month)-1, data=bankdata,
                family=binomial(link="logit"))
bank.clog= glm(Churn~as.factor(Month)-1, data=bankdata,
               family=binomial(link="cloglog"))
```

```{r}
plot(bank.logit$coefficients,type='l')
plot(bank.clog$coefficients,type='l')
```

```{r}
##Below, we are adding month i.e. we are doing monotone 
bankdata$Month2 = bankdata$Month^2
bank.logit= glm(Churn~Month+Age+Income+HomeVal+Tenure+
                  DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                family=binomial(link="logit"))

summary(bank.logit)
```


```{r}
#For constant baseline 


bank.logit1 = glm(Churn~Age+Income+HomeVal+Tenure+
                    DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                  family=binomial(link="logit"))
bank.clog1 = glm(Churn~Age+Income+HomeVal+Tenure+
                   DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                 family=binomial(link="cloglog"))
summary(bank.logit1)
summary(bank.clog1)
```

```{r}
#For monotone baseline 

bank.logit2 = glm(Churn~Month+Age+Income+HomeVal+Tenure+
                    DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                  family=binomial(link="logit"))
bank.clog2 = glm(Churn~Month+Age+Income+HomeVal+Tenure+
                   DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                 family=binomial(link="cloglog"))

summary(bank.logit2)
summary(bank.clog2)
```


```{r}
# non-monotone baseline

bank.logit3 = glm(Churn~poly(Month,2)+Age+Income+HomeVal+Tenure+
                    DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                  family=binomial(link="logit"))
bank.clog3 = glm(Churn~poly(Month,2)+Age+Income+HomeVal+Tenure+
                   DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                 family=binomial(link="cloglog"))
AIC(bank.logit1)
AIC(bank.logit2)
AIC(bank.logit3)
BIC(bank.logit1)
BIC(bank.clog2)
BIC(bank.clog3)
```

```{r}
## Discrete Hazard Model
bank.logit= glm(Churn~as.factor(Month)+Age+Income+HomeVal+Tenure+
                  DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                family=binomial(link="logit"))
bank.logit= glm(Churn~as.factor(Month)+Age+Income+HomeVal+Tenure+
                  DirectDeposit+Loan+NumAccounts+Dist+MktShare , data=bankdata,
                family=binomial(link="cloglog"))
summary(bank.logit)

AIC(bank.logit1)
AIC(bank.logit2)
AIC(bank.logit3)
AIC(bank.logit)
BIC(bank.logit1)
BIC(bank.clog2)
BIC(bank.clog3)
BIC(bank.logit)
```




